ms2

### 2017-04-28 ms2/ms2.Rmd
updated

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
import::from(pander, pander)
import::from(broom, tidy)
```

@@

```{r fnz-mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=fnz, color=region, label=state_abbreviation)) +
geom_point() +
geom_label(nudge_x=0.05) +
xlab('claims per beneficiary') +
ylab('fraction of beneficiaries w/ >= 1 claim') +
theme_minimal()
```

@@

```{r nzgini-mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=nzgini, color=region, label=state_abbreviation)) +
geom_point() +
geom_label(nudge_x=0.05) +
xlab('claims per beneficiary') +
ylab('Gini coefficient among benes. w/ >= 1 claim') +
theme_minimal()
```

@@

@@

```{r ecoli_quin, cache=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Escherichia coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
import::from(pander, pander)
import::from(broom, tidy)
```

@@

```{r fnz-mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=fnz, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('fraction of beneficiaries w/ >= 1 claim') +
theme_minimal()
```

@@

```{r nzgini-mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=nzgini, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('Gini coefficient among benes. w/ >= 1 claim') +
theme_minimal()
```

@@

And what about looking at multivariate only for ones that passed the threshold for univariate? Doesn't seem like it works for any of them!

```{r}
sig_bug_drug = results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r ecoli_quin, cache=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Escherichia coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()

left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Escherichia coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='black', se=FALSE) +
  geom_point() +
  geom_text() +
  xlim(0.2, 0.45) + ylim(0, 50) +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

Bactrim resistance in *E. coli*. First, the aggregate relationship, then the relationship between "excess" resistance (the residual of resistance against aggregate consumption) against nonzero Gini.

```{r ecoli_bactrim}
ecoli_bactrim_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Escherichia coli', drug_group=='tmp_smx') %>%
  filter(!is.na(mean_percent_nonsusceptible))

ecoli_bactrim_dat %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  scale_x_continuous(limits=c(0.08, 0.2), breaks=c(0.08, 0.1, 0.15, 0.2)) +
  ylim(10, 45) +
  xlab('TMP/SMX claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()

ecoli_bactrim_dat %>%
  { mutate(., excess_resistance=residuals(lm(mean_percent_nonsusceptible ~ mean, data=.))) } %>%
  ggplot(aes(x=nzgini, y=excess_resistance)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  scale_x_continuous(limits=c(0.25, 0.375)) +
  scale_y_continuous(limits=c(-12, 20), breaks=c(-12, 0, 10, 20)) +
  xlab('Skew towards high consumers (Gini coefficient)') +
  ylab('"Excess" E. coli resistance (see caption)') +
  theme_minimal()
```
